---
title: "week9"
author: "Dana Tomeh"
date: "3/22/2020"
output: pdf_document
params:
    output_dir: "../output"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Volumes/GoogleDrive/My Drive/Classes/2019-2020 (Third Year)/Spring 2020/Data Science/Week 9/week9")
```

 **Libraries**
```{r, message=FALSE}
library(tidyverse)
library(ggplot2)
library(lubridate)
```

 **Data Import**
```{r}
week9_tbl <-as_tibble(read_csv("../data/week3.csv")) %>%
  mutate(Q1Q5means =rowMeans(week9_tbl[5:9]), Q6Q10means=rowMeans(week9_tbl[10:14]))
```
*data imported as a tibble 
*Column Q1Q5means was added that contains the means of the responses on Q1 to Q5  for each person in the dataset
*Column Q6Q10means was added that contains the means of the responses on Q6 to Q10  for each person in the dataset

**Visualization**
```{r, echo=FALSE}
ggplot(week9_tbl_2, aes(Q1Q5means, Q6Q10means))+
  geom_point() + 
  geom_smooth(method="lm", se=FALSE)
```
This plot contains the means of questions 1 through 5 plotted against the means of questions 6 through ten. 

**Analysis**
```{r}
cor.test(week9_tbl_2$Q1Q5means, week9_tbl_2$Q6Q10means)
```
The correlation was -.14 (p>.05), which is not statistically significant.