---
title: "week9"
author: "Dana Tomeh"
date: "3/22/2020"
output: pdf_document
params:
    output_dir: "../output"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Volumes/GoogleDrive/My Drive/Classes/2019-2020 (Third Year)/Spring 2020/Data Science/Week 9/week9")
```

 **Libraries**
```{r, include=FALSE}
library(tidyverse)
library(ggplot2)
library(lubridate)
```

 **Data Import**
 
 *data imported as a tibble 
*Column Q1Q5means was added that contains the means of the responses on Q1 to Q5  for each person in the dataset
*Column Q6Q10means was added that contains the means of the responses on Q6 to Q10  for each person in the dataset
```{r}
week9_tbl <- as_tibble(read_csv("../data/week3.csv"))
  
week9_tbl_clean <- week9_tbl %>%
  mutate(timeStart=ymd_hms(timeStart),
         gender=factor(gender,levels=c("M","F"),labels=c("Male","Female")),
         condition=factor(condition,levels=c("A","B","C"), labels=c("Block A","Block B","Control")),
         Q1Q5means =rowMeans(week9_tbl[5:9]),
         Q6Q10means=rowMeans(week9_tbl[10:14])) %>%
  filter(q6==1)
```


**Visualization**
```{r, echo=FALSE}
ggplot(week9_tbl_clean, aes(Q1Q5means, Q6Q10means))+
  geom_point() + 
  geom_smooth(method="lm", se=FALSE)+
  labs(x="Mean of Q1 to Q5",
       y="Mean of Q6 to Q10",
       title="Mean of Q1 to Q5 versus Mean of Q6 to Q10")
```
This plot contains the means of questions 1 through 5 plotted against the means of questions 6 through ten. 

**Analysis**
```{r}
mean_cor <- cor.test(week9_tbl_clean$Q1Q5means, week9_tbl_clean$Q6Q10means)
mean_cor$estimate
mean_cor$p.value
```
The correlation was `mean_cor$p.value` and (p= `mean_cor$p.value`), which is not statistically significant.